Insurance choice, decision assistance, and insurer steering

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
update ashecon slides and summary figures

- What's new here?
  - Role of decision assistance in health
  - Public and private decision assistance in the same market
  - Commissions and steering

@@

- Public decision assistance in the form of "navigators"
- Private brokers and agents (majority are brokers)

>>>>

- What's new here?
  - Role of decision assistance in health insurance choice
  - Public and private decision assistance in the same market
  - Commissions and steering

@@

- Public decision assistance in the form of "navigators", no commissions
- Private assistance that receives commissions:
  - "certified insurance agent", acts as independent broker (97%)
  - "plan-based enroller", acts as agent for insurer (3%)
  - all listed as "agent" in our analysis
